### 2022-03-29 GB_Simulation_3Species.Rmd
Created scripts, again
small changes
d
changes resolution of temp maps

#LOAD HABITAT PREVIOUSLY CREATED
hab <- readRDS(file="hab_justYT.RDS")

@@

@@

moveCov <- readRDS(file="20 year moveCov matrices/GeorgesBank/GB_22yr_ConstTemp_HaddockStrata")

>>>>

#LOAD HABITAT PREVIOUSLY CREATED
#hab <- readRDS(file="hab_justYT.RDS") #finer resolution
hab <- readRDS(file="hab_justYT2.RDS") #courser resolution

@@

#rebuild package
devtools::build()

@@

#moveCov <- readRDS(file="20 year moveCov matrices/GeorgesBank/GB_22yr_ConstTemp_HaddockStrata")
moveCov <- readRDS(file="20 year moveCov matrices/GeorgesBank/GB_22yr_ConstTemp_HaddockStrata_res2")
